Modelling and Analysis of an Elevator System with NuSMV2

### 2013-06-07 paper/main.tex
paper: spellchecking

	In this elaboration of the exercise on NuSMV2 for the Radboud University Nijmegen course ``Analysis of Embedded Systems'' we enumerate our notes and solutions for each problem. Besides this elaboration we have submitted the generated models and templates for these models by e-mail. For problem 4 and 5 we've written an application that measures the executiontime for a specific model in NuSMV. The sources for this application, this report and the models can be found on Github at \url{http://github.com/Wassasin/elevatormodel}.

@@

	Some macros are defined to increase the readability of the model. It can be seen that transition rules often have to be defined for each user or floor seperately. We have not found a way to express this more conveniently, so we ended up with writing a simple script that generates NuSMV models for a variable number of users and floors.

@@

	For this analysis we wrote a tool that generates a model for a specific number of floor and users, and measures the executiontime of that model in NuSMV2. If the modelchecker runs for more than 2 minutes, the attempt is terminated. Below we enumerate the executiontime in seconds for each instance of a model.

@@

	The following properties have all succesfully been verified.

>>>>

	In this elaboration of the exercise on NuSMV2 for the Radboud University Nijmegen course ``Analysis of Embedded Systems'' we enumerate our notes and solutions for each problem. Besides this elaboration we have submitted the generated models and templates for these models by e-mail. For problem 4 and 5 we've written an application that measures the execution time for a specific model in NuSMV. The sources for this application, this report and the models can be found on Github at \url{http://github.com/Wassasin/elevatormodel}.

@@

	Some macros are defined to increase the readability of the model. It can be seen that transition rules often have to be defined for each user or floor separately. We have not found a way to express this more conveniently, so we ended up with writing a simple script that generates NuSMV models for a variable number of users and floors.

@@

	For this analysis we wrote a tool that generates a model for a specific number of floor and users, and measures the execution time of that model in NuSMV2. If the model checker runs for more than 2 minutes, the attempt is terminated. Below we enumerate the execution time in seconds for each instance of a model.

@@

	The following properties have all successfully been verified.
